\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-18 paper/paper 2/dc-2015.tex
3.1

A cornerstone of the framework is the generic representation of a constraint, which can often be done using \emph{Description Logics (DL)} \cite{Kroetzsch2012,Baader-2003,Baader-Nutt-2003}, as for the \emph{minimum qualified cardinality restrictions}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person.}}  This way, the knowledge representation formalism DL with its well-studied theoretical properties provides the foundational basis for the framework.

>>>>

A cornerstone of the framework is the generic representation of a constraint, which can often be done using Description Logics, as for the \emph{minimum qualified cardinality restriction} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person.}}  This way, the knowledge representation formalism \emph{Description Logics (DL)} \cite{Kroetzsch2012,Baader-2003,Baader-Nutt-2003} with its well-studied theoretical properties provides the foundational basis for the framework.
